Refinements for open automata

### 2021-12-03 2021-Refinement/paper/refinementarticle.tex
transistivity proof 1) and 2)

We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of open automata.
\begin{enumerate}
\item $R_{13}$ satisfies initial configurations. By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to. We have:
\begin{align*}
\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}&\implies\\
R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
 \end{align*}
Hence we get:
\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
\item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
\[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]

@@

On one side, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exist an indexed family of OTs originating from $s_{2p}$: 
\begin{align*}
\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
\end{align*}
such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} 
\end{multline*}		
that can be re-written:
\begin{multline*}
%\everymath{\displaystyle}
\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} \\
	\end{multline*}	
\medskip
Adding to the two terms of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \land\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
		\end{array}} \\
\end{align*}

On the other side, according the relation between $A_2$ and $A_3$ we have for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$:
\begin{align*}
\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}
\end{align*}
there exist an indexed family of OTs originating from $s_3$: 
\begin{align*}
\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
\end{align*}
such that $\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ and
\begin{multline*}
\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\\hspace{2em} \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}} 
\end{multline*}
that can be re-written:
\begin{multline*}
\everymath{\displaystyle}
\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}
\cap H'} \!\!\fvars{\beta_{2pxj}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}} 
\end{multline*}
The following  can be derived from the two previous cases: \\
$\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion\\
$\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
In addition, we get: \\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy} \cap H'} \!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  
$
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj}  \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \\
		\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}	
		\end{array}} 
\end{align*}		
With the restriction of the domain and the simplification of the formula, we get:\\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H\cap H'} \!\!\!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  
$
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{align*}

Because of the domain of the substitutions of the relations, we have:
\begin{align*}
\underbrace{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}_{R_{13}\mpar{s_1, s_3}} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{R_{12}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{align*}	
This allows us to conclude, with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$:

$\forall p \in P, \forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H'),$\\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}}, $
\begin{align*}
R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
\hspace{7.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p \in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \\\wedge g_{3pxy}\wedge \\
{R_{12}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
\end{array}}
\end{align*}	
This provides the desired conclusion:\\
$\forall z \in Z,  J'_1 \cap (H \cap H') = J'_{3z} \cap (H\cap H')$\\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}} ,  $
\begin{align*}
\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap H'} \beta_{1j}=\beta_{3jz}\\ \wedge g_{3z}\wedge 
{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
\end{array}}}
\end{align*}	
\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
\begin{multline*}
 V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \right)
\end{multline*}
that can be rewritten:
\begin{align*}
R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
\end{align*}
By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
\begin{align*}
R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
\end{align*}
Yet according to the relation between $A_1$ and $A_2$ we have  forall $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
\begin{multline*}
 V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash \left(R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
Then,
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
\end{align*}
The desired result will be obtained by transitivity of

>>>>

We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of open automata.
\begin{enumerate}
\item $R_{13}$ satisfies initial configurations. By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to. We have:
\begin{align*}
\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}&\implies\\
R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{\implies R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
 \end{align*}
Hence we get:
\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
\item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
\[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]

@@

On one side, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
\begin{align*}
\OTx{1}{}{1}{1} \in \fOT{s_1}
\end{align*}
there exist an indexed family of OTs originating from $s_{2p}$: 
\begin{align*}
\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
\end{align*}
such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} 
\end{multline*}		
that can be re-written:
\begin{multline*}
%\everymath{\displaystyle}
\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
		\end{array}}} \\
	\end{multline*}	
\medskip
Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \land\\
			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
		\end{array}} \\
\end{align*}

On the other side, according the relation between $A_2$ and $A_3$ we have for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$:
\begin{align*}
\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}
\end{align*}
there exist an indexed family of OTs originating from $s_3$: 
\begin{align*}
\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
\end{align*}
such that $\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ and
\begin{multline*}
\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\\hspace{2em} \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}} 
\end{multline*}
that can be re-written:
\begin{multline*}
\everymath{\displaystyle}
\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}
\cap H'} \!\!\fvars{\beta_{2pxj}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}} 
\end{multline*}
The following  can be derived from the two previous cases: \\
$\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion\\
$\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
In addition, we get: \\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy} \cap H'} \!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  
$
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj}  \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \\ 
\land
		\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
		\end{array}}	
		\end{array}} 
\end{align*}		
With the restriction of the domain and the simplification of the formula, we get:\\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H\cap H'} \!\!\!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  
$
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{align*}

Because of the domain of the substitutions of the relations, we have:
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{align*}

This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$. We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.

\begin{multline*}
\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}

This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition \TODO{re-write the set of OTs or not?} with (note that $\psi_{2px}$ has no effect on variables of $A1$ and $A3$:
\begin{multline*}
R_{13}(s_1,s_3)  \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}

\TODO{[LUDO] je suis un peu embete par le fait qu on se soit debarrasse des quantifiers et qu ils reviennent miraculeusement ici, a completer ou au moins commeter a mon avis (1footnote peut suffire si on est bien convaincus)}
This provides the desired conclusion:\\
$\forall z \in Z,  J'_1 \cap (H \cap H') = J'_{3z} \cap (H\cap H')$\\
$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}} ,  $
\begin{align*}
\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap H'} \beta_{1j}=\beta_{3jz}\\ \wedge g_{3z}\wedge 
{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
\end{array}}}
\end{align*}	
\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
\begin{multline*}
 V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \right)
\end{multline*}
that can be rewritten:
\begin{align*}
R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
\end{align*}
By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
\begin{align*}
R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
\end{align*}
Yet according to the relation between $A_1$ and $A_2$ we have  forall $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
\begin{multline*}
 V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash \left(R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
Then,
\begin{align*}
R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
\end{align*}
The desired result will be obtained by transitivity of
